### 2020-04-07 3_implementation.tex
Add addition text and prune case study section.

We have implemented Task Bench in the 15 parallel and distributed
programming systems listed in Table~\ref{tab:systems}. These include
traditional HPC programming models (MPI and MPI+X), PGAS and actor
models (Chapel, Charm++ and X10), task-based systems (OmpSs, OpenMP
4.0, PaRSEC, Realm, Regent, and StarPU) and systems for large scale
data analytics, machine learning and workflows (Dask, Spark, Swift/T,
and TensorFlow). We briefly describe the systems and implementations
below.

>>>>

We have implemented Task Bench in the 15 parallel and distributed
programming systems listed in Table~\ref{tab:systems}. These include
traditional HPC programming models (MPI and MPI+X), PGAS and actor
models (Chapel, Charm++ and X10), task-based systems (OmpSs, OpenMP
4.0, PaRSEC, Realm, Regent, and StarPU) and systems for large scale
data analytics, machine learning and workflows (Dask, Spark, Swift/T,
and TensorFlow). Implementing Task Bench in such a wide range of
systems is possible because the separation between core API (in
Table~\ref{tab:api}) and system implmentation enables an overall
effort of $\mathcal{O}(m + n)$ (for $m$ benchmarks on $n$ systems)
rather than $\mathcal{O}(mn)$ as has been the case for all previous
benchmarks that we know of. We briefly describe the systems and
implementations below.

### 2020-04-07 7_conclusion.tex
Small tweak.
Add addition text and prune case study section.

Task Bench is a new approach for evaluating the performance of
parallel and distributed programming systems. By separating the
specification of a benchmark from implementations in various
programming systems, it is possible to explore a broad space of
application scenarios and to do so with a large number of programming
systems. Our experiments have enabled the following
insights:

@@

Not considered in our analysis is the impact of programming system
features on programmer productivity and performance portability. Most
applications do not operate at the absolute extreme of runtime-limited
performance, and thus may choose to trade overhead for better
usability. Our study helps to quantify the performance side of that
tradeoff so that users can be better informed and developers can see
the impact that features have on the performance of their programming
systems.

>>>>

Task Bench is a new approach for evaluating the performance of
parallel and distributed programming systems. By separating the
specification of a benchmark from implementations in various
programming systems, Task Bench reduces overall developer effort to
$\mathcal{O}(m + n)$ (for $m$ benchmarks on $n$ systems) rather than
$\mathcal{O}(mn)$ as has been the case for all previous
benchmarks that we know of. This has enabled us to explore a broad space of
application scenarios and to do so with a large number of programming
systems. Our experiments have enabled the following
insights:

@@

Not considered in our analysis is the impact of programming system
features on programmer productivity and performance portability. Most
applications do not operate at the absolute extreme of runtime-limited
performance, and thus may choose to trade overhead for
usability. Our study helps to quantify the performance side of that
tradeoff so that users can be better informed and developers can see
the impact that features have on the performance of their programming
systems.

### 2020-04-07 8_case_study.tex
Add addition text and prune case study section.

Task Bench is useful not only as a tool for evaluating programming
system performance, but also for discovering potential areas of
improvements. During the development of Task Bench, we identified a
number of performance issues in the underlying programming
systems. These discoveries were possible because of the flexibility of
Task Bench, and our ability to rapidly run new experiments with a
variety of application scenarios. All issues below have been reported
to and acknowledged by the respective system's developers, and are
either fixed or worked around in our experiments.

Realm and Chapel use DMA subsystems that are optimized for large
copies. Early Task Bench experiments revealed high METG values that
were diagnosed by the Realm/Chapel developers as overhead due to the
cost of scheduling small copies. Subsequent improvements in Realm and
Chapel improved small copy overheads (and thus METG) by over an order
of magnitude in the case of Realm, and by $2\times$ in the case of
Chapel. These improvements affect any application where fine-grained
tasks are used.

Further analysis of Realm efficiency indicated many overheads due to
dynamic graph construction. The Realm developers implemented a new
``subgraph'' API in response to this feedback to amortize the cost of
repeatedly constructing isomorphic task graphs. This API is used in
Task Bench to achieve further speedups in the Realm implementation.

@@

Initial experiments with TensorFlow revealed that the TensorFlow Task
Bench implementation was not able to use all cores on a node (thus
making it impossible to measure METG since the efficiency was below
50\%). The TensorFlow developers diagnosed this as an issue in
constant folding. The entire Task Bench task graph was being detected
as constant, and the constant-folding pass runs on one core. As a
workaround, the developers suggested marking the task graph inputs as
non-constant so that TensorFlow's standard task scheduler could be
used.

>>>>

Task Bench is useful not only as a tool for evaluating programming
system performance, but also for discovering potential areas of
improvements. During the development of Task Bench, we identified a
number of performance issues in the underlying programming
systems. These discoveries were possible because of the flexibility of
Task Bench, and our ability to rapidly run new experiments with a
variety of application scenarios. All issues were reported to and
acknowledged by the respective system's developers, and are either
fixed or worked around in our experiments. For brevity, we describe
one salient example below and summarize the others briefly.

Realm and Chapel both use DMA subsystems that are optimized for large
copies. Early Task Bench experiments revealed high METG values that
were diagnosed by the Realm/Chapel developers as overhead due to the
cost of scheduling small copies. Subsequent improvements in Realm and
Chapel improved small copy overheads (and thus METG) by over an order
of magnitude in the case of Realm, and by $2\times$ in the case of
Chapel. These improvements affect any application where fine-grained
tasks are used, which is particularly relevant in strong scaling
regimes when running on large numbers of nodes.

We found further areas for improvement in schedulers (Realm, Chapel
and Dask), task pruning for scalability (PaRSEC), and optimizations on
the task graph (TensorFlow). The impact of these optimizations ranged
from small constant factors to even asymptotic improvements in
performance and scalability (in the case of PaRSEC and Dask). All
users will benefit from the improvements driven by our discoveries.

\zap{
Further analysis of Realm efficiency indicated many overheads due to
dynamic graph construction. The Realm developers implemented a new
``subgraph'' API in response to this feedback to amortize the cost of
repeatedly constructing isomorphic task graphs. This API is used in
Task Bench to achieve further speedups in the Realm implementation.

@@

Initial experiments with TensorFlow revealed that the TensorFlow Task
Bench implementation was not able to use all cores on a node (thus
making it impossible to measure METG since the efficiency was below
50\%). The TensorFlow developers diagnosed this as an issue in
constant folding. The entire Task Bench task graph was being detected
as constant, and the constant-folding pass runs on one core. As a
workaround, the developers suggested marking the task graph inputs as
non-constant so that TensorFlow's standard task scheduler could be
used.
}
